Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-10 Paper/paper.tex
Converted to IEEE format

%&pdflatex
\documentclass{article}

\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{geometry}
\usepackage{todonotes}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

 \newenvironment{Figure}
  {\par\medskip\noindent\minipage{\linewidth}}
  {\endminipage\par\medskip}

@@

\graphicspath{{./images/}}
\setlength{\parskip}{0pt}

\begin{document}
\maketitle
\begin{multicols}{2}
\abstract{
  Internet topology has been measured and modeled for many years, but few studies  quantify how the topology changes over time.\Ben[inline]{This is not true, there are many studies of the evolution of the AS Internet. We should be more specificy about what this statement means, ie with respect to national boundaries}.  Over the past decade, governments around the world have recognized that the Internet is a powerful tool for controlling and surveilling their citizens, and they have begun enacting common policies for ASes operating within their borders.

@@

This paper extends earlier research on AS topology and BGP simulation to study chokepoints across the Internet over multiple years, using our
path simulation and routing tree datasets to view snapshots of the Internet
over multiple years. We provide comprehensive and accessible tools for studying
the complex and dynamic AS level Internet topology. Through this approach we
can more carefully evaluate the state of the Internet than was previously possible.}

@@

\begin{Figure}
	\centering
	\includegraphics[width=\linewidth]{chokepoint}
	\captionof{figure}{Chokepoint potential example. ASes A,B, and C are all border nodes. 
						AS D is an internal node. ASes E and F are both external nodes.
						The out-to-in chokepoint potentials of A,B, and C are 0.25, 0.25, and 0.5 respectively.}\label{fig:chokepoint}
\end{Figure}

@@

\begin{Figure}
	\centering
	\includegraphics[width=\linewidth]{single_CN}
	\captionof{figure}{The evolution of China's in-to-out Chokepoint Potential}\label{fig:ChinaChokePoint}
\end{Figure}

\begin{Figure}
	\centering
	\includegraphics[width=\linewidth]{single_US}
	\captionof{figure}{The evolution of the US's Chokepoint Potential}\label{fig:USChokePoint}
\end{Figure}

@@

\begin{Figure}
	\centering
	\includegraphics[width=\linewidth]{single_DE}
	\captionof{figure}{The evolution of Germany's in-to-out Chokepoint Potential}\label{fig:GermChokePoint}
\end{Figure}

@@

\begin{Figure}
	\centering
	\includegraphics[width=\linewidth]{NodesNeeded}
	\captionof{figure}{Number of ASes to intercept 90\% of ito paths for multiple nations over time}\label{fig:nodes}
\end{Figure}

@@

\begin{Figure}
	\centering
	\includegraphics[width=\linewidth]{fotn2017}
	\captionof{figure}{Number of ASes to intercept 90\% of ito paths vs Freedom On The Net Score (2017)}\label{fig:fotn2017}
\end{Figure}

@@

\end{multicols}

>>>>

%&pdflatex
\documentclass[10pt, conference, letterpaper]{IEEEtran}

\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{todonotes}

@@

\graphicspath{{./images/}}

\begin{document}
\maketitle
\begin{abstract}{.Internet topology has been measured and modeled for many years, but few studies  quantify how the topology changes over time.\Ben[inline]{This is not true, there are many studies of the evolution of the AS Internet. We should be more specificy about what this statement means, ie with respect to national boundaries}.  Over the past decade, governments around the world have recognized that the Internet is a powerful tool for controlling and surveilling their citizens, and they have begun enacting common policies for ASes operating within their borders.

@@

This paper extends earlier research on AS topology and BGP simulation to study chokepoints across the Internet over multiple years, using our
path simulation and routing tree datasets to view snapshots of the Internet
over multiple years. We provide comprehensive and accessible tools for studying
the complex and dynamic AS level Internet topology. Through this approach we
can more carefully evaluate the state of the Internet than was previously possible.}
\end{abstract}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{chokepoint}
	\caption{Chokepoint potential example. ASes A,B, and C are all border nodes. 
						AS D is an internal node. ASes E and F are both external nodes.
						The out-to-in chokepoint potentials of A,B, and C are 0.25, 0.25, and 0.5 respectively.}\label{fig:chokepoint}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{single_CN}
	\caption{The evolution of China's in-to-out Chokepoint Potential}\label{fig:ChinaChokePoint}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{single_US}
	\caption{The evolution of the US's Chokepoint Potential}\label{fig:USChokePoint}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{single_DE}
	\caption{The evolution of Germany's in-to-out Chokepoint Potential}\label{fig:GermChokePoint}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{NodesNeeded}
	\caption{Number of ASes to intercept 90\% of ito paths for multiple nations over time}\label{fig:nodes}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fotn2017}
	\caption{Number of ASes to intercept 90\% of ito paths vs Freedom On The Net Score (2017)}\label{fig:fotn2017}
\end{figure}

@@
